---
title: "Life Expectancy Report"
output: html_document
---
```{r setup, include = FALSE}
# `analysis.R`を実行して結果をロードする
# `include = FALSE`が指定されているためエラーやメッセージは表示されない
source("analysis.R")

# `knitr`ライブラリをロードする
library("knitr")
```

## Overview
This is a brief report regarding life expectancy for each country from
1960 to 2015 ([source](https://data.worldbank.org/indicator/SP.DYN.LE00.IN)).
The data reveals that the country with the longest life expectancy was
`r longest_le$Country.Name`, with a life expectancy of `r longest_le$expectancy`.
That life expectancy was `r le_difference` years longer than the life expectancy
in `r shortest_le$Country.Name`.
Here are the countries whose life expectancy **improved the most** since 1960.

```{r top_10_gain, echo = FALSE}
# top_10_tableをkable()で表示する
# この時、表示する列を指定する
kable(top_10_gain, col.names = c("Country", "Change in Life Expectancy"))
```

## Life Expectancy in 2015
To identify geographic variations in life expectancy,
here is a choropleth map of life expectancy in 2015:

```{r le_map, echo = FALSE}
# `rworldmap`パッケージを用いて地図をレンダリングする
mapCountryData(
  mapped_data, # indicate the data to map
  mapTitle = "Life Expectancy in 2015",
  nameColumnToPlot = "X2015",
  addLegend = F, # exclude the legend
  colourPalette = brewer.pal(7, "Blues") # set the color palette
)
```
